---
title: "AF_Correlation_Regression_Modeling_4.4.18"
author: "cmosle1"
date: "4/4/2018"
output: html_document
---

```{r}
#data import. 

AFdata<- read.csv("C:/Users/cwbishop/Documents/dropbox/Dropbox/Work/UW BandBlab/Studies/eHearing/AF_US_UNI_AllSubsSurvey+Audio_2.20.18.csv", header=T, na.strings="#NULL!")
#head(AFdata)
#View(AFdata)

library("dplyr")
library("tidyr")
library("ggplot2")
library('caTools')
library("Hmisc")
library("foreign")
library("nnet")
library("reshape2")
library(gridExtra)
```


#Changing "90NR" and "9999" to "95"; Copied from previous code (AF_MI1_3.9.18.rmd)
```{r}

#issue with 90NR --> 95 change: the HHT doesn't measure other thresholds if 90NR at 1000Hz (first threshold tested). Should we set all thresholds to 95 or leave them missing? ---> SOLUTION: SET ALL >90 to 95

#Changing 90NR (aka 9999) and Conventional audio thresholds that are > 90 to 95

#Left Ear
AFdata$L5<-AFdata$L500
AFdata$L5[AFdata$L500 > 90] <- 95
AFdata$L1<-AFdata$L1000
AFdata$L1[AFdata$L1000 > 90] <- 95
AFdata$L2<-AFdata$L2000
AFdata$L2[AFdata$L2000 > 90] <- 95
AFdata$L4<-AFdata$L4000
AFdata$L4[AFdata$L4000 > 90] <- 95


#Right Ear
AFdata$R5<-AFdata$R500
AFdata$R5[AFdata$R500 > 90] <- 95
AFdata$R1<-AFdata$R1000
AFdata$R1[AFdata$R1000 > 90] <- 95
AFdata$R2<-AFdata$R2000
AFdata$R2[AFdata$R2000 > 90] <- 95
AFdata$R4<-AFdata$R4000
AFdata$R4[AFdata$R4000 > 90] <- 95

#At 8000Hz
AFdata$L8<-AFdata$L8000
AFdata$L8[AFdata$L8000 > 90] <- 95
AFdata$R8<-AFdata$R8000
AFdata$R8[AFdata$R8000 > 90] <- 95
```


# Creating PTA Values (L, R, & BE); Copied from previous code (AF_MI1_3.9.18.rmd)
```{r}
# Calculating PTA in each ear

#colnames(AFdata[,1000:1021])
AFdata$LPTA <- apply(AFdata[,1011:1014], 1, mean, na.rm=T)
AFdata$RPTA <- apply(AFdata[,1015:1018], 1, mean, na.rm=T)


AFdata$LPTA[is.nan(AFdata$LPTA)]  <- NA
AFdata$RPTA[is.nan(AFdata$RPTA)]  <- NA

#Now can calculate BEPTA (PTA in better ear)
AFdata$BEPTA<- ifelse((!is.na(AFdata$RPTA) & AFdata$RPTA <= AFdata$LPTA) | is.na(AFdata$LPTA),
                      AFdata$RPTA, AFdata$LPTA)
#To Check
#AFdata[c(1,2,257),c("RPTA", "LPTA", "BEPTA")] 
#is.na(AFdata$BEPTA)
#AFdata[which(is.na(AFdata$RPTA)), c("RPTA", "LPTA", "BEPTA")]
```

# Relevant Questions
 #q0001- Participant ID
 #q0002- Gender; 1=F
 #q0003- Age: 1= under 60; 2= 60-64; 3=65-69; 4= 70-74; 5= 75-79; 6= 80-84' 70= 85+
 #q0005- marital status: 1=married/committed relationship; 2= single/divorced/widowed/never married
 #q0008- highest grade completed: 1= none; 2=elementary; 3= secondary; 4-undergrad; 5= graduate
 #q0010- household income
 #q0012- do health benefits cover cost of a hearing test
 #q0013- do health benefits cover cost of hearing aids
 #q0014- race: 1= American indian; 2= Asian; 3= White; 4= Native Hawaiian/PI; 5= Black/AA; 6=More than               one race
 #q0018_0001- In general, would you say your health is: 1= Exellent, 2= Very Good, 3= Good, 4=Fair, 5=Poor
 #q0020_0001- In general would you say your quality of life is: 1=Excellent, 5 = Poor
 #q0030_0015- Have you ever been told by a doctor or HCP that you have hearing loss?
 #q0030_0016- Have you ever been told by a doctor or HCP that you have vision loss? 
 #q0030_0017- Have you ever been told by a doctor or HCP that you have balance problems or dizziness?
 #q0032- Are you deaf or do you have a significant hearing difficulty? 1=Yes; 2=No
 #q0034- Do your ever get noises such as ringing or buzzing in your ears or head (tinnitus) that last         more than 5 minutes? (If yes) Do you get these noises some of the time, most of the time, or         all of the time? 1=No; 2=Yes, some of the time; 3= Yes, most or all of the time
 #q0036- Have you ever worked in a place that was so noisy you had to shout to be heard? 1=No; 2= Yes,         < 1 year; 3=Yes, for 1-5 years; 4= Yes, > 5 years
 #q0042- Do you have a hearing problem now? 1= Yes; 2= No
 #q0046- Pathway question: 1-3= No hearing problem; 4= Hearing loss, no treatment; 5= Hearing loss + treatment
 

#Reducing size of dataset
```{r}
abbrev.data <- select(AFdata , c("q0002", "q0003", "q0005", "q0008", "q0010", "q0012", "q0013", "q0014", "q0018_0001", "q0020_0001","q0032", "q0034", "q0036", "q0042", "q0046", "BEPTA"))

AFdata$q0020_0001
```


#Correlation Matrix using Pearson's r & sig levels
```{r}
AFcorr1 <- rcorr(as.matrix(abbrev.data))
AFcorr1
```

## Variables significantly correlated with BEPTA include:
   q0002 q0003 q0008 q0012 q0013 q0018_0001 q0032 q0042 q0046

## Ranked by magnitude of correlation
   q0046, q0032, q0042, q0003, q0013, q0012, q0002, q0018_0001, q0008




#Splitting sample

```{r}
set.seed(4) 
samp.split1 <- sample.split(AFdata$q0001, SplitRatio = .5)
temp_mangroup <- subset(AFdata, samp.split1 == TRUE) #Will use this group to generate model after taking out NA's for BEPTA
testgroup  <- subset(AFdata, samp.split1 == FALSE) #Will test model on them after it's created
mangroup <-drop_na(temp_mangroup, c('BEPTA')) #Will use this group to generate model
dim(mangroup) # n=248
dim(testgroup) # n=261
is.na(mangroup$BEPTA) #No missing PTA values
identical(testgroup, mangroup) #Shows me that this group is different from the one I used in my Amelia model
```


#Parsing down split sample
```{r}
man.group1 <- select(mangroup , c("q0002", "q0003", "q0005", "q0008", "q0010", "q0012", "q0013", "q0014", "q0018_0001", "q0032", "q0034", "q0036", "q0042", "q0046", "BEPTA"))

```

# Starting forward selection process (FS)

```{r}

## Variables significantly correlated with BEPTA include:
   #q0002 q0003 q0008 q0012 q0013 q0018_0001 q0032 q0042 q0046

## Ranked by magnitude of correlation
   #q0046, q0032, q0042, q0003, q0013, q0012, q0002, q0018_0001, q0008


fs1<- lm(BEPTA~q0046, data=man.group1)
summary(fs1)

fs2<- lm(BEPTA ~ q0046 + q0032, data=man.group1)
summary(fs2)

fs3<- lm(BEPTA ~ q0046 + q0032 + q0042, data=man.group1) #higher R-squared but q0042 is not significant
summary(fs3)

fs4<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003, data=man.group1) #higher R-squared and all are significant
summary(fs4)

fs5<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0013, data=man.group1) #higher R-squared but q0013 isn't significant
summary(fs5)

fs6<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0013 + q0012, data=man.group1) #higher R-squared but q0012 isn't significant (essentially the same as having q0013 in)
summary(fs6)

fs7<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0013 + q0012 + q0002, data=man.group1) #higher R-squared but q0013, q0012, or q0002 aren't significant.Not substantially increasing R-squared
summary(fs7)

fs8<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0013 + q0012 + q0002 + q0018_0001, data=man.group1) #higher R-squared but q0013, q0012, or q0002 aren't significant.Not substantially increasing R-squared
summary(fs8)

fs9<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0013 + q0012 + q0002 + q0018_0001 + q0008, data=man.group1) #higher R-squared but q0013, q0012, or q0002 aren't significant.Not substantially increasing R-squared
summary(fs9)
```


# Backward selection process

```{r}
## Variables significantly correlated with BEPTA include:
   #q0002 q0003 q0008 q0012 q0013 q0018_0001 q0032 q0042 q0046

## Ranked by magnitude of correlation
   #q0046, q0032, q0042, q0003, q0013, q0012, q0002, q0018_0001, q0008

bs1<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0013 + q0012 + q0002 + q0018_0001 + q0008, data=man.group1) 
summary(bs1)

bs2<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0012 + q0002 + q0018_0001 + q0008, data=man.group1) 
summary(bs2) #very slight increase in R-squared value when q0013 deleted (.5587 --> .5588)

bs3<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0002 + q0018_0001 + q0008, data=man.group1) 
summary(bs3) #reduction in R-squared value when q0012 deleted (.5588 --> .5553)

bs3<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0018_0001 + q0008, data=man.group1) 
summary(bs3) #no change in R-squared value when q0002 deleted compared to bs3 (still .5553)

bs4<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0008, data=man.group1) 
summary(bs4) #slight improvement in R-squared compared to bs3 when q0018_0001 deleted (.5553 --> .5565)

bs5<- lm(BEPTA ~ q0046 + q0032 + q0003 + q0008, data=man.group1) 
summary(bs5) #slight reduction in R-squared with q0042 deleted (.5565 --> .5525)

bs6<- lm(BEPTA ~ q0046 + q0032 + q0003, data=man.group1) 
summary(bs6) #slight reduction in R-squared with q0008 deleted (.5525 --> .5416)

bs7<- lm(BEPTA ~ q0046 + q0032, data=man.group1) 
summary(bs7) #large reduction with q0003 removed (.5416 --> .4385)

bs8<- lm(BEPTA ~ q0046, data=man.group1) 
summary(bs8) #large reduction with q0032 removed (.4385 --> .3739)

```


# Relevant Questions
 #q0001- Participant ID
 #q0002- Gender; 1=F
 #q0003- Age: 1= under 60; 2= 60-64; 3=65-69; 4= 70-74; 5= 75-79; 6= 80-84 70= 85+
 #q0005- marital status: 1=married/committed relationship; 2= single/divorced/widowed/never married
 #q0008- highest grade completed: 1= none; 2=elementary; 3= secondary; 4-undergrad; 5= graduate
 #q0010- household income
 #q0012- do health benefits cover cost of a hearing test
 #q0013- do health benefits cover cost of hearing aids
 #q0014- race: 1= American indian; 2= Asian; 3= White; 4= Native Hawaiian/PI; 5= Black/AA; 6=More than               one race
 #q0018_0001- In general, would you say your health is: 1= Exellent, 2= Very Good, 3= Good, 4=Fair, 5=Poor
 #q0020_0001- In general would you say your quality of life is: 1=Excellent, 5 = Poor
 #q0030_0015- Have you ever been told by a doctor or HCP that you have hearing loss?
 #q0030_0016- Have you ever been told by a doctor or HCP that you have vision loss? 
 #q0030_0017- Have you ever been told by a doctor or HCP that you have balance problems or dizziness?
 #q0032- Are you deaf or do you have a significant hearing difficulty? 1=Yes; 2=No
 #q0034- Do your ever get noises such as ringing or buzzing in your ears or head (tinnitus) that last         more than 5 minutes? (If yes) Do you get these noises some of the time, most of the time, or         all of the time? 1=No; 2=Yes, some of the time; 3= Yes, most or all of the time
 #q0036- Have you ever worked in a place that was so noisy you had to shout to be heard? 1=No; 2= Yes,         < 1 year; 3=Yes, for 1-5 years; 4= Yes, > 5 years
 #q0042- Do you have a hearing problem now? 1= Yes; 2= No
 #q0046- Pathway question: 1-3= No hearing problem; 4= Hearing loss, no treatment; 5= Hearing loss + treatment



# Generating best model based on fs and bs processes
```{r}
bm1<- lm(BEPTA ~ q0046 + q0032 + q0003 + q0012, data=man.group1)
summary(bm1)

bm2<- lm(BEPTA ~ q0046 + q0032 + q0003 + q0012 + q0008, data=man.group1)
summary(bm2)

bm3<- lm(BEPTA ~ q0046 + q0032 + q0003 + q0008, data=man.group1)
summary(bm3)

bm4<- lm(BEPTA ~ q0046 + q0032 + q0003 + q0008 + q0042, data=man.group1)
summary(bm4)

bm5<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0012 + q0002 + q0008, data=man.group1) 
summary(bm5) #Best model I could create so far. Took the best model from the backward selection process and took out q0018, which caused an improvement in R-square when it was removed. I also tried taking out q0002, but it reduced the R-squared.

```


# Relevant Questions
 #q0001- Participant ID
 #q0002- Gender; 1=F
 #q0003- Age: 1= under 60; 2= 60-64; 3=65-69; 4= 70-74; 5= 75-79; 6= 80-84' 70= 85+
 #q0005- marital status: 1=married/committed relationship; 2= single/divorced/widowed/never married
 #q0008- highest grade completed: 1= none; 2=elementary; 3= secondary; 4-undergrad; 5= graduate
 #q0010- household income
 #q0012- do health benefits cover cost of a hearing test
 #q0013- do health benefits cover cost of hearing aids
 #q0014- race: 1= American indian; 2= Asian; 3= White; 4= Native Hawaiian/PI; 5= Black/AA; 6=More than one race
 #q0018_0001- In general, would you say your health is: 1= Exellent, 2= Very Good, 3= Good, 4=Fair, 5=Poor
 #q0020_0001- In general would you say your quality of life is: 1=Excellent, 5 = Poor
 #q0030_0015- Have you ever been told by a doctor or HCP that you have hearing loss?
 #q0030_0016- Have you ever been told by a doctor or HCP that you have vision loss? 
 #q0030_0017- Have you ever been told by a doctor or HCP that you have balance problems or dizziness?
 #q0032- Are you deaf or do you have a significant hearing difficulty? 1=Yes; 2=No
 #q0034- Do your ever get noises such as ringing or buzzing in your ears or head (tinnitus) that last         more than 5 minutes? (If yes) Do you get these noises some of the time, most of the time, or         all of the time? 1=No; 2=Yes, some of the time; 3= Yes, most or all of the time
 #q0036- Have you ever worked in a place that was so noisy you had to shout to be heard? 1=No; 2= Yes,         < 1 year; 3=Yes, for 1-5 years; 4= Yes, > 5 years
 #q0042- Do you have a hearing problem now? 1= Yes; 2= No
 #q0046- Pathway question: 1-3= No hearing problem; 4= Hearing loss, no treatment; 5= Hearing loss + treatment
 


#Testing best model fit from the manipulated group on non-observed group (testgroup)--TGmodels

```{r}
tgmod1<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0012 + q0002 + q0008, data=testgroup) 
summary(tgmod1) #R-squared is higher for this one compared to the manipulation group used for bs & fs
```


#Same forward selection process (FSel), but for test group
```{r}
test.group1 <- select(testgroup , c("q0002", "q0003", "q0005", "q0008", "q0010", "q0012", "q0013", "q0014", "q0018_0001", "q0032", "q0034", "q0036", "q0042", "q0046", "BEPTA"))


## Variables significantly correlated with BEPTA include:
   #q0002 q0003 q0008 q0012 q0013 q0018_0001 q0032 q0042 q0046

## Ranked by magnitude of correlation
   #q0046, q0032, q0042, q0003, q0013, q0012, q0002, q0018_0001, q0008


fsel1<- lm(BEPTA~q0046, data=test.group1)
summary(fsel1) #Rsquared = .418

fsel2<- lm(BEPTA ~ q0046 + q0032, data=test.group1)
summary(fsel2) #Rsquared= .504

fsel3<- lm(BEPTA ~ q0046 + q0032 + q0042, data=test.group1) #q0042 doesn't add to model; also not-significant
summary(fsel3)

fsel4<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003, data=test.group1) 
summary(fsel4)

fsel5<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0013, data=test.group1) 
summary(fsel5)

fsel6<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0013 + q0012, data=test.group1) #lower R-squared with q0012 added
summary(fsel6)

fsel7<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0013 + q0012 + q0002, data=test.group1) #adding q0002 improved r-squared
summary(fsel7)

fsel8<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0013 + q0012 + q0002 + q0018_0001, data=test.group1) #q0018 reduces r-squared
summary(fsel8)

fsel9<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0013 + q0012 + q0002 + q0018_0001 + q0008, data=test.group1) #slight improvement with q0008 added
summary(fsel9)

```



#Same backward selection process (BSel), but for test group
```{r}
bsel1<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0013 + q0012 + q0002 + q0018_0001 + q0008, data=test.group1) 
summary(bsel1)

bsel2<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0012 + q0002 + q0018_0001 + q0008, data=test.group1) 
summary(bsel2) #slight reductiion in r-squared with q0013 removed

bsel3<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0002 + q0018_0001 + q0008, data=test.group1) #minimal change in r-square (-.001)
summary(bsel3) 

bsel3<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0018_0001 + q0008, data=test.group1) #slight reduction in r-square
summary(bsel3) 

bsel4<- lm(BEPTA ~ q0046 + q0032 + q0042 + q0003 + q0008, data=test.group1) #increase in r-square with q0018 removed
summary(bsel4) 

bsel5<- lm(BEPTA ~ q0046 + q0032 + q0003 + q0008, data=test.group1) #slight increase in r-square with q0042 removed
summary(bsel5) 

bsel6<- lm(BEPTA ~ q0046 + q0032 + q0003, data=test.group1) #slight reduction with q0008 removed
summary(bsel6) 

bsel7<- lm(BEPTA ~ q0046 + q0032, data=test.group1) #large reduction with q0003 removed
summary(bsel7) 

bsel8<- lm(BEPTA ~ q0046, data=test.group1) #large reduction with q0032 removed
summary(bsel8) 

```



#Visualizing the models
```{r}
# Grab residuals
tgres <- residuals(tgmod1)
# Convert to DataFrame for gglpot
tgres <- as.data.frame(tgres)
ggplot(tgres,aes(tgres)) +  geom_histogram(fill='blue',alpha=0.5)


mgres <- residuals(bm5)
mgres <- as.data.frame(mgres)
ggplot(mgres,aes(mgres)) +  geom_histogram(fill='red',alpha=0.5)

plot(tgmod1) #test group
plot(bm5) #manipulation group
```


# Checking prediction accuracy 
```{r}
tg.predictions <- predict(tgmod1,test.group1)

#Now we can get the root mean squared error, a standardized measure of how off we were with our predicted values:

results <- cbind(tg.predictions,test.group1$BEPTA) 
colnames(results) <- c('pred','real')
results <- as.data.frame(results)

plot(results$real,results$pred)
cor.test(results$real, results$pred)

summary(lm(results$real~results$pred))

  # DIFFICULTY WITH THIS FUNCTION. WONT WORK
to_zero<- function(x){
    if  (x < 0){
        return(0)
    }else{
        return(x)
    }
}

results$pred <- sapply(results$pred, to_zero)

#Mean Squared Error
mse <- mean((results$real-results$pred)^2)
print(mse)


mse^0.5



#results$diff<- results$pred - results$real
#mean.diff<- mean(results$diff, na.rm=T)

```


Changing PTA from continuous to categorical
```{r}
#ASHA Standards: (0)Normal: -10-25; (1)Mild: 26-40; (2)Moderate: 41-55; (3)Moderately-Severe: 56-70; (4)Severe: 71-90; (5)Profound: >90

results$pred.deg <- cut(results$pred,
                  breaks=c(-Inf, 25, 40, 55, 70, 90, Inf),
                  labels=c("0", "1", "2", "3", "4", "5"))

results$real.deg <- cut(results$real,
                  breaks=c(-Inf, 25, 40, 55, 70, 90, Inf),
                  labels=c("0", "1", "2", "3", "4", "5"))

results.deg<-cbind(results$pred.deg, results$real.deg)
colnames(results.deg) <-c('pred.deg', 'real.deg')
results.deg<-as.data.frame  (results.deg)

#Comparing predicted vs. real degree of hearing loss
View(results.deg)
results.deg$diff <- (results.deg$pred.deg - results.deg$real.deg)
sum(results.deg$diff, na.rm=T)


#Look at ROC curve

```


Re-running regression analysis with categorical variables instead of interval
```{r}
table(AFdata$q0046)

bestmod.cat<- lm(BEPTA ~ factor(q0046) + factor(q0032,levels=c(2,1)) + factor(q0042,levels=c(2,1)) + factor(q0003) + factor(q0012) + factor(q0002) + factor(man.group1$q0008,levels=c(5,4,3)), data=man.group1) 
summary(bestmod.cat)
```


Determining which categories should be our reference points
```{r}
# Relevant Questions
 #q0001- Participant ID
 #q0002- Gender; 1=F, 2=M
 #q0003- Age: 1= under 60; 2= 60-64; 3=65-69; 4= 70-74; 5= 75-79; 6= 80-84; 7= 85+
 #q0005- marital status: 1=married/committed relationship; 2= single/divorced/widowed/never married
 #q0008- highest grade completed: 1= none; 2=elementary; 3= secondary; 4-undergrad; 5= graduate
 #q0010- household income
 #q0012- do health benefits cover cost of a hearing test
 #q0013- do health benefits cover cost of hearing aids
 #q0014- race: 1= American indian; 2= Asian; 3= White; 4= Native Hawaiian/PI; 5= Black/AA; 6=More than one race
 #q0018_0001- In general, would you say your health is: 1= Exellent, 2= Very Good, 3= Good, 4=Fair, 5=Poor
 #q0020_0001- In general would you say your quality of life is: 1=Excellent, 5 = Poor
 #q0030_0015- Have you ever been told by a doctor or HCP that you have hearing loss?
 #q0030_0016- Have you ever been told by a doctor or HCP that you have vision loss? 
 #q0030_0017- Have you ever been told by a doctor or HCP that you have balance problems or dizziness?
 #q0032- Are you deaf or do you have a significant hearing difficulty? 1=Yes; 2=No
 #q0034- Do your ever get noises such as ringing or buzzing in your ears or head (tinnitus) that last         more than 5 minutes? (If yes) Do you get these noises some of the time, most of the time, or         all of the time? 1=No; 2=Yes, some of the time; 3= Yes, most or all of the time
 #q0036- Have you ever worked in a place that was so noisy you had to shout to be heard? 1=No; 2= Yes,         < 1 year; 3=Yes, for 1-5 years; 4= Yes, > 5 years
 #q0042- Do you have a hearing problem now? 1= Yes; 2= No
 #q0046- Pathway question: 1-3= No hearing problem; 4= Hearing loss, no treatment; 5= Hearing loss + treatment


#q0008-- 5 should be reference (graduate)
#q0010-- 1 should be reference (under $20K)
#q0012-- 1 should be reference (yes)
#q0013-- 1 should be reference (yes)
#q0014-- 3 should be reference (white)
#q0032-- 2 should be reference (no)
#q0034-- 1 should be reference (no)
#q0036-- 1 should be reference (no)
#q0042-- 2 should be reference (no)
#q0046 (aka pathway) -- 1 should be reference (no hearing problem)


#collapsing q0046 into 3 categories where 1= no hearing problem (pathway 1), 4= hearing loss no help (pathway 2), & 5= hearing loss + help (pathway 3)
AFdata$pathway <-ifelse(AFdata$q0046== 1 | AFdata$q0046== 2 | AFdata$q0046==3, 1, AFdata$q0046)
table (AFdata$pathway)


#base code for setting reference groups

bpathway<- factor(AFdata$pathway, levels = c(5, 1, 4)) #put reference group FIRST!

pracreg2<-lm(BEPTA~bpathway, data=AFdata)
summary(pracreg2)

man.group1$pathway <-ifelse(man.group1$q0046== 1 | man.group1$q0046== 2 | man.group1$q0046==3, 1, man.group1$q0046)
```

#Run LM between each variable & continuous BEPTA. Determine significance based on adjusted R-square. FS & BS on maninpulation group. After getting best model, run it on test group. Then use degree of hearing loss.
```{r}

pathway_model <- lm(pathway ~factor(q0032,levels=c(2,1)) + factor(q0042,levels=c(2,1)) + factor(q0003) + factor(q0012) + factor(q0002) + factor(man.group1$q0008,levels=c(5,4,3)), data=man.group1) 
summary(pathway_model)

#collapse pathway question
man.group1$pathway <-ifelse(man.group1$q0046== 1 | man.group1$q0046== 2 | man.group1$q0046==3, 1, man.group1$q0046)

tgmod1<- lm(BEPTA ~  factor(pathway)+ factor(q0032,levels=c(2,1)) +  factor(q0042,levels=c(2,1)) + factor(q0003) + factor(q0012) + factor(q0002) + factor(q0008,levels=c(5,4,3)), data=man.group1) 
tg.predictions <- predict(tgmod1,test.group1)

#Now we can get the root mean squared error, a standardized measure of how off we were with our predicted values:

results <- cbind(tg.predictions,test.group1$BEPTA) 
colnames(results) <- c('pred','real')
results <- as.data.frame(results)

plot(results$real,results$pred,xlim=c(0,500))
plot(results$real.deg,results$pred.deg)
cor.test(results$real, results$pred)

summary(lm(results$real~results$pred))

#ASHA Standards: (0)Normal: -10-25; (1)Mild: 26-40; (2)Moderate: 41-55; (3)Moderately-Severe: 56-70; (4)Severe: 71-90; (5)Profound: >90

results$pred.deg <- cut(results$pred,
                  breaks=c(-Inf, 25, 40, 55, 70, 90, Inf),
                  labels=c("0", "1", "2", "3", "4", "5"))

results$real.deg <- cut(results$real,
                  breaks=c(-Inf, 25, 40, 55, 70, 90, Inf),
                  labels=c("0", "1", "2", "3", "4", "5"))

results.deg<-cbind(results$pred.deg, results$real.deg)
colnames(results.deg) <-c('pred.deg', 'real.deg')
results.deg<-as.data.frame  (results.deg)

#Comparing predicted vs. real degree of hearing loss
View(results.deg)
results.deg$diff <- (results.deg$pred.deg - results.deg$real.deg)
sum(results.deg$diff, na.rm=T)
plot(results.deg$diff,na.rm=T)


plot(results.deg$real.deg,results.deg$pred.deg)
ggplot(results.deg,aes(x=real.deg,y=pred.deg)) + geom_point(alpha = 0.05)

grid.table(with(results.deg,table(real=real.deg,pred=pred.deg)))

plot(results$real,results$pred,xlim = c(0,100))

### Linear regression is not appropriate for pathway variable. Use nominal regression

pathway_nom_model <- multinom(pathway ~factor(q0032,levels=c(2,1)) + factor(q0042,levels=c(2,1)) + factor(q0003) + factor(q0012) + factor(q0002) + factor(q0008,levels=c(5,4,3)), data=man.group1) 
summary(pathway_nom_model)
z <- summary(pathway_nom_model)$coefficients/summary(pathway_nom_model)$standard.errors
z
p <- (1 - pnorm(abs(z), 0, 1)) * 2
p
```
