---
title: "AF_Correlation_Regression_Modeling_9.5.18"
author: "cmosle1"
date: "4/4/2018"
output: html_document
---

```{r}
#data import. 

#AFdata<- read.csv("~/Desktop/eHearing/Modeling Literature/AF_US_UNI_AllSubsSurvey+Audio_2.20.18.csv", header=T, na.strings="#NULL!")

AFdata<- read.csv("C:/Users/cwbishop/Documents/dropbox/Dropbox/Work/UW BandBlab/Studies/eHearing/AF_US_UNI_AllSubsSurvey+Audio_2.20.18.csv", header=T, na.strings="#NULL!")
#head(AFdata)
#View(AFdata)

library("dplyr")
library("tidyr")
library("ggplot2")
library('caTools')
library("Hmisc")
library("boot")
library("gridExtra")
library("MASS")
library("MuMIn")

```


#Changing "90NR" and "9999" to "95"; Copied from previous code (AF_MI1_3.9.18.rmd)
```{r}

#issue with 90NR --> 95 change: the HHT doesn't measure other thresholds if 90NR at 1000Hz (first threshold tested). Should we set all thresholds to 95 or leave them missing? ---> SOLUTION: SET ALL >90 to 95

#Changing 90NR (aka 9999) and Conventional audio thresholds that are > 90 to 95
AFdata <- AFdata[-which(names(AFdata) == "RPTA")]
#Left Ear
AFdata$L5<-AFdata$L500
AFdata$L5[AFdata$L500 > 90] <- 95
AFdata$L1<-AFdata$L1000
AFdata$L1[AFdata$L1000 > 90] <- 95
AFdata$L2<-AFdata$L2000
AFdata$L2[AFdata$L2000 > 90] <- 95
AFdata$L4<-AFdata$L4000
AFdata$L4[AFdata$L4000 > 90] <- 95


#Right Ear
AFdata$R5<-AFdata$R500
AFdata$R5[AFdata$R500 > 90] <- 95
AFdata$R1<-AFdata$R1000
AFdata$R1[AFdata$R1000 > 90] <- 95
AFdata$R2<-AFdata$R2000
AFdata$R2[AFdata$R2000 > 90] <- 95
AFdata$R4<-AFdata$R4000
AFdata$R4[AFdata$R4000 > 90] <- 95

#At 8000Hz
AFdata$L8<-AFdata$L8000
AFdata$L8[AFdata$L8000 > 90] <- 95
AFdata$R8<-AFdata$R8000
AFdata$R8[AFdata$R8000 > 90] <- 95
```


# Creating PTA Values (L, R, & BE); Copied from previous code (AF_MI1_3.9.18.rmd)
```{r}
# Calculating PTA in each ear

#colnames(AFdata[,1000:1021])
AFdata$LPTA <- apply(AFdata[,c('L5','L1','L2','L4')], 1, mean, na.rm=T)
AFdata$RPTA <- apply(AFdata[,c('R5','R1','R2','R4')], 1, mean, na.rm=T)


AFdata$LPTA[is.nan(AFdata$LPTA)]  <- NA
AFdata$RPTA[is.nan(AFdata$RPTA)]  <- NA

#Now can calculate BEPTA (PTA in better ear)
AFdata$BEPTA<- ifelse((!is.na(AFdata$RPTA) & AFdata$RPTA <= AFdata$LPTA) | is.na(AFdata$LPTA),
                      AFdata$RPTA, AFdata$LPTA)

AFdata$hcat<- cut(AFdata$BEPTA,
                  breaks=c(-Inf, 25, 40, 55, Inf),
                  labels=c("1", "2", "3","4"))
#To Check
#AFdata[c(1,2,257),c("RPTA", "LPTA", "BEPTA")] 
#is.na(AFdata$BEPTA)
#AFdata[which(is.na(AFdata$RPTA)), c("RPTA", "LPTA", "BEPTA")]
```

# Relevant Questions
 #q0001- Participant ID
 #q0002- Gender; 1=F
 #q0003- Age: 1= under 60; 2= 60-64; 3=65-69; 4= 70-74; 5= 75-79; 6= 80-84' 70= 85+
 #q0005- marital status: 1=married/committed relationship; 2= single/divorced/widowed/never married
 #q0008- highest grade completed: 1= none; 2=elementary; 3= secondary; 4-undergrad; 5= graduate
 #q0010- household income
 #q0012- do health benefits cover cost of a hearing test
 #q0013- do health benefits cover cost of hearing aids
 #q0014- race: 1= American indian; 2= Asian; 3= White; 4= Native Hawaiian/PI; 5= Black/AA; 6=More than               one race
 #q0018_0001- In general, would you say your health is: 1= Exellent, 2= Very Good, 3= Good, 4=Fair, 5=Poor
 #q0020_0001- In general would you say your quality of life is: 1=Excellent, 5 = Poor
 #q0030_0015- Have you ever been told by a doctor or HCP that you have hearing loss?
 #q0030_0016- Have you ever been told by a doctor or HCP that you have vision loss? 
 #q0030_0017- Have you ever been told by a doctor or HCP that you have balance problems or dizziness?
 #q0032- Are you deaf or do you have a significant hearing difficulty? 1=Yes; 2=No
 #q0034- Do your ever get noises such as ringing or buzzing in your ears or head (tinnitus) that last         more than 5 minutes? (If yes) Do you get these noises some of the time, most of the time, or         all of the time? 1=No; 2=Yes, some of the time; 3= Yes, most or all of the time
 #q0036- Have you ever worked in a place that was so noisy you had to shout to be heard? 1=No; 2= Yes,         < 1 year; 3=Yes, for 1-5 years; 4= Yes, > 5 years
 #q0042- Do you have a hearing problem now? 1= Yes; 2= No
 #q0046- Pathway question: 1-3= No hearing problem; 4= Hearing loss, no treatment; 5= Hearing loss + treatment
 

#Reducing size of dataset
```{r}
abbrev.data <- dplyr::select(AFdata , c("q0002", "q0003", "q0005", "q0008", "q0010", "q0012", "q0013", "q0014", "q0018_0001", "q0020_0001","q0032", "q0034", "q0036", "q0042", "q0046", "BEPTA"))


```


Determining which categories should be our reference points
```{r}
# Relevant Questions
 #q0001- Participant ID
 #q0002- Gender; 1=F, 2=M
 #q0003- Age: 1= under 60; 2= 60-64; 3=65-69; 4= 70-74; 5= 75-79; 6= 80-84' 70= 85+
 #q0005- marital status: 1=married/committed relationship; 2= single/divorced/widowed/never married
 #q0008- highest grade completed: 1= none; 2=elementary; 3= secondary; 4-undergrad; 5= graduate
 #q0010- household income
 #q0012- do health benefits cover cost of a hearing test
 #q0013- do health benefits cover cost of hearing aids
 #q0014- race: 1= American indian; 2= Asian; 3= White; 4= Native Hawaiian/PI; 5= Black/AA; 6=More than one race
 #q0018_0001- In general, would you say your health is: 1= Exellent, 2= Very Good, 3= Good, 4=Fair, 5=Poor
 #q0020_0001- In general would you say your quality of life is: 1=Excellent, 5 = Poor
 #q0030_0015- Have you ever been told by a doctor or HCP that you have hearing loss?
 #q0030_0016- Have you ever been told by a doctor or HCP that you have vision loss? 
 #q0030_0017- Have you ever been told by a doctor or HCP that you have balance problems or dizziness?
 #q0032- Are you deaf or do you have a significant hearing difficulty? 1=Yes; 2=No
 #q0034- Do your ever get noises such as ringing or buzzing in your ears or head (tinnitus) that last         more than 5 minutes? (If yes) Do you get these noises some of the time, most of the time, or         all of the time? 1=No; 2=Yes, some of the time; 3= Yes, most or all of the time
 #q0036- Have you ever worked in a place that was so noisy you had to shout to be heard? 1=No; 2= Yes,         < 1 year; 3=Yes, for 1-5 years; 4= Yes, > 5 years
 #q0042- Do you have a hearing problem now? 1= Yes; 2= No
 #q0046- Pathway question: 1-3= No hearing problem; 4= Hearing loss, no treatment; 5= Hearing loss + treatment


#q0008-- 5 should be reference (graduate)
#q0010-- 1 should be reference (under $20K)
#q0012-- 1 should be reference (yes)
#q0013-- 1 should be reference (yes)
#q0014-- 3 should be reference (white)
#q0032-- 2 should be reference (no)
#q0034-- 1 should be reference (no)
#q0036-- 1 should be reference (no)
#q0042-- 2 should be reference (no)
#q0046 (aka pathway) -- 1 should be reference (no hearing problem)


#collapsing q0046 into 3 categories where 1= no hearing problem (pathway 1), 4= hearing loss no help (pathway 2), & 5= hearing loss + help (pathway 3)
AFdata$pathway <-ifelse(AFdata$q0046== 1 | AFdata$q0046== 2 | AFdata$q0046==3, 1, AFdata$q0046)
table (AFdata$pathway)


#base code for setting reference groups

bpathway<- factor(AFdata$pathway, levels = c(5, 1, 4)) #put reference group FIRST!

#pracreg2<-lm(BEPTA~bpathway, data=AFdata)
#summary(pracreg2)

```

#Run LM between each variable & continuous BEPTA. Determine significance based on adjusted R-square. FS & BS on maninpulation group. After getting best model, run it on test group. Then use degree of hearing loss.







Bootstrap model creation and prediction on different sample sets

```{r}
#Create function to split data, train model, and test model prediction without output being correlation value
model_boot <- function(){
samp.split2 <- sample.split(AFdata$q0001, SplitRatio = .5)
temp_mangroup2 <- subset(AFdata, samp.split2 == TRUE) #Will use this group to generate model after taking out NA's for BEPTA
testgroup2  <- subset(AFdata, samp.split2 == FALSE) #Will test model on them after it's created
mangroup2<-drop_na(temp_mangroup2, c('BEPTA')) #Will use this group to generate model
dim(mangroup2) # n=248
dim(testgroup2) # n=261
is.na(mangroup2$BEPTA) #No missing PTA values
identical(testgroup2, mangroup2)

# Train model
bestmod1.2<- lm(formula = BEPTA ~ factor(q0046) + factor(q0032, levels = c(2,1)) + factor(q0042, levels = c(2, 1)) + factor(q0003) + factor(q0002), data = testgroup2)
# Test model prediction
testgroup2.predictions <- predict(bestmod1.2,testgroup2)

#Now we can get the root mean squared error, a standardized measure of how off we were with our predicted values:

results2 <- cbind(testgroup2.predictions,testgroup2$BEPTA) 
colnames(results2) <- c('pred','real')
results2 <- as.data.frame(results2)

#plot(results2$real,results2$pred)
cor <- cor(results2$real, results2$pred, use='complete.obs', method='pearson')
cor
}

#Run function 1000 times and record correlation values
#out <- replicate(1000,model_boot())
#hist(out)
```

Automated ordinal regression model selection
```{r}
# Convert hcat into an ordered factor
#AFdata$hcat <- factor(AFdata$hcat,levels=c(1:4),ordered=TRUE)
#AFdata$q0046 <- as.factor(AFdata$q0046)
#AFdata$q0032 <- as.factor(AFdata$q0032)


#Remove rows with missing hcat values
#auto_or_data <- AFdata[complete.cases(AFdata$hcat),]
#auto_or_data <- auto_or_data[complete.cases(auto_or_data$q0046),]
#auto_or_data <- auto_or_data[complete.cases(auto_or_data$q0032),]

#x <- auto_or_data[,c('q0046','q0032')]
#y <- auto_or_data$hcat
#fit <- glmpathcr(x,y)
#summary(fit)

#plot(fit, xvar = "step", type = "bic")
#plot(fit, xvar = "step", type = "coefficients")

#USE DREDGE

```


Training Ordinal regression model
```{r}
AFdata$hcat <- factor(AFdata$hcat,levels=c(1:4),ordered=TRUE)
ormod_data <- AFdata[,c('hcat','q0046','q0032','q0042','q0003','q0002')]
ormod_data <- ormod_data[complete.cases(ormod_data),]

ormod <- polr(hcat~factor(q0046) + factor(q0032, levels = c(2,1)) + factor(q0042, levels = c(2, 1)) + factor(q0003) + factor(q0002), data = ormod_data, Hess=TRUE)

summary(ormod)
ortable <- coef(summary(ormod))
p <- pnorm(abs(ortable[,"t value"]),lower.tail=FALSE)*2
ortable <- cbind(ortable,'p value'=p)
ci <- confint(ormod)
exp(coef(ormod))
exp(cbind(OR=coef(ormod),ci))
ortable
```

```{r}
# Bootstrap model selection when split into train and test set. Use prediction correlation as best model parameter.
options(na.action = "na.fail") 

#Create model with all variables
boot_ormod_data <- AFdata[,c('hcat','q0002','q0003','q0008','q0012','q0013','q0018_0001','q0032','q0042','q0046')]
boot_ormod_data <-  boot_ormod_data[complete.cases(boot_ormod_data),]

# Split data into train and test sets.
model_boot_split <- function(){
samp.split2 <- sample.split(boot_ormod_data$q0002, SplitRatio = .7)
mangroup2 <- subset(boot_ormod_data, samp.split2 == TRUE) #Will use this group to generate model after taking out NA's for BEPTA
testgroup2  <- subset(boot_ormod_data, samp.split2 == FALSE) #Will test model on them after it's created
identical(testgroup2, mangroup2)

# Input total model with all predictors
#boot_ormod_all <- polr(hcat~factor(q0002)+factor(q0003)+factor(q0008) +factor(q0012)+factor(q0013)+ factor(q0018_0001)+factor(q0032, levels = c(2,1)) + factor(q0042, levels = c(2, 1)) +factor(q0046), data = mangroup2, Hess=TRUE)

boot_ormod_all <- polr(hcat~factor(q0002)+ factor(q0032, levels = c(2,1)) + factor(q0042, levels = c(2, 1))+factor(q0046), data = mangroup2, Hess=TRUE)

dredge_results <- dredge(boot_ormod_all)

dredge_best <- get.models(dredge_results, subset = 1)[[1]]
# Test model prediction
testgroup2.predictions <- predict(dredge_best,testgroup2)

#Now we can get the root mean squared error, a standardized measure of how off we were with our predicted values:

results2 <- cbind(testgroup2.predictions,testgroup2$hcat) 
colnames(results2) <- c('pred','real')
results2 <- as.data.frame(results2)

#plot(results2$real,results2$pred)
cor <- cor(results2$real, results2$pred, use='complete.obs', method='pearson')

#cor
out=c(dredge_best,cor)
}

#boot_out <- replicate(1000,model_boot_split())
#hist(unlist(boot_out[seq(0,length(boot_out),20)]))
#mean(unlist(boot_out[seq(0,length(boot_out),20)]))
#quantile(unlist(boot_out[seq(0,length(boot_out),20)]))

  


grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0002))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0003))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0008))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0012))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0013))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0018_0001))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0032))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0042))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0046))

```




# Explore overlap between q46 and q32. 


```{r}
AUS_data<- read.csv("C:/Users/cwbishop/Documents/dropbox/Dropbox/Work/UW BandBlab/Studies/eHearing/AF_AU_UNI_Survey+HT_12.13.17.csv", header=T, na.strings=c("#NULL!",'90NR'))

CAN_data<- read.csv("C:/Users/cwbishop/Documents/dropbox/Dropbox/Work/UW BandBlab/Studies/eHearing/AF_CAN_InPerson_AllSubs_Survey+Audio_CLEAN_07.25.2018.csv", header=T, na.strings=c("#NULL!",'90NR'))

UK_data<- read.csv("C:/Users/cwbishop/Documents/dropbox/Dropbox/Work/UW BandBlab/Studies/eHearing/AF_UK_InPerson_AllSurvey+AllAudios_CLEAN_7.26.18.csv", header=T, na.strings=c("#NULL!",'90NR'))

US_data<- read.csv("C:/Users/cwbishop/Documents/dropbox/Dropbox/Work/UW BandBlab/Studies/eHearing/AF_US_UNI_AllSubsSurvey+Audio_2.20.18.csv", header=T, na.strings=c("#NULL!",'90NR'))

#Loop to convert thresholds to BEPTA, then to HL categories. 

data_prep <- function(data){
    
#If thresholds are not numeric convert to numeric.

if(class(data$L1000) != 'integer'){data[,c('L500','L1000','L2000','L4000','R500','R1000','R2000','R4000')] <- as.numeric(as.character(data[,c('L500','L1000','L2000','L4000','R500','R1000','R2000','R4000')]))
}

#issue with 90NR --> 95 change: the HHT doesn't measure other thresholds if 90NR at 1000Hz (first threshold tested). Should we set all thresholds to 95 or leave them missing? ---> SOLUTION: SET ALL >90 to 95

    #Changing 90NR (aka 9999) and Conventional audio thresholds that are > 90 to 95
#Left Ear

data$L5<-data$L500
data$L5[data$L500 > 90] <- 95
data$L1<-data$L1000
data$L1[data$L1000 > 90] <- 95
data$L2<-data$L2000
data$L2[data$L2000 > 90] <- 95
data$L4<-data$L4000
data$L4[data$L4000 > 90] <- 95


#Right Ear
data$R5<-data$R500
data$R5[data$R500 > 90] <- 95
data$R1<-data$R1000
data$R1[data$R1000 > 90] <- 95
data$R2<-data$R2000
data$R2[data$R2000 > 90] <- 95
data$R4<-data$R4000
data$R4[data$R4000 > 90] <- 95

#At 8000Hz
data$L8<-data$L8000
data$L8[data$L8000 > 90] <- 95
data$R8<-data$R8000
data$R8[data$R8000 > 90] <- 95

# Calculating PTA in each ear

#colnames(data[,1000:1021])
data$LPTA <- apply(data[,c('L5','L1','L2','L4')], 1, mean, na.rm=T)
data$RPTA <- apply(data[,c('R5','R1','R2','R4')], 1, mean, na.rm=T)


data$LPTA[is.nan(data$LPTA)]  <- NA
data$RPTA[is.nan(data$RPTA)]  <- NA

#Now can calculate BEPTA (PTA in better ear)
data$BEPTA<- ifelse((!is.na(data$RPTA) & data$RPTA <= data$LPTA) | is.na(data$LPTA),
                      data$RPTA, data$LPTA)

data$hcat<- cut(data$BEPTA,
                  breaks=c(-Inf, 25, 40, 55, Inf),
                  labels=c("1", "2", "3","4"))
return(data)
}

UK_data <- data_prep(UK_data)
CAN_data <- data_prep(CAN_data)
AUS_data <- data_prep(AUS_data)
US_data <- data_prep(US_data)


# Explore pathway resonse vs hcat
grid.table(table(UK_data$hcat,UK_data$q0046))
grid.table(table(CAN_data$hcat,CAN_data$q0046))
grid.table(table(US_data$hcat,US_data$q0046))
grid.table(table(AUS_data$hcat,AUS_data$q0046))

# Explore pathway response vs deaf 


pathway_response <- function(data){
#Explore pathway 5+ normal hearing people. Only works with US data. Partially works with UK. Other countries have too few in pathway 5, Normal hearing
pathway5_group <- data[which(data$q0046==5 & data$hcat==1),]


tab_137 <-  matrix(table(pathway5_group$q0137),dimnames=list(c('yes','no'),'Do you wear a cochlear implant or other surgically implanted hearing device'))
tab_141 <- matrix(table(pathway5_group$q0141),dimnames=list(c('yes','no'),'Do you use hearing aids or other hearing devices?'))

#*Think about how much you used your present hearing aids or other hearing devices over the past two weeks. On an average day, how many hours did you use them?

tab_142 <- matrix(table(pathway5_group$q0142),dimnames=list(c('none','<1','1-4','4-8','8+'),'On an average day, how many hours did you use them?'))
                  
#Check each of the following devices that you have used to help you hear better.

tab_151_1 <- matrix(table(pathway5_group$q0151_0001))
names(tab_151_1) <- 'phone with volume control'
tab_151_1

tab_151_2 <- matrix(table(pathway5_group$q0151_0002))
names(tab_151_2) <- 'headphones for the tv'
tab_151_2

tab_151_3 <- matrix(table(pathway5_group$q0151_0002))
names(tab_151_3) <- 'computer'
tab_151_3

tab_151_4 <- matrix(table(pathway5_group$q0151_0004))
names(tab_151_4) <- 'smartphone '
tab_151_4

tab_151_5 <- matrix(table(pathway5_group$q0151_0005))
names(tab_151_5) <- 'alarm clock'
tab_151_5

tab_151_6 <- matrix(table(pathway5_group$q0151_0006))
names(tab_151_6) <- 'alerting device for doorbell'
tab_151_6
tab_151_7 <- matrix(table(pathway5_group$q0151_0007))
names(tab_151_7) <- 'iPad'
tab_151_7
tab_151_8 <- matrix(table(pathway5_group$q0151_0008))
names(tab_151_8) <- 'personal amp'
tab_151_8
tab_151_9 <- matrix(table(pathway5_group$q0151_0009))
names(tab_151_9) <- 'closed captioning'
tab_151_9



## Where did you get your hearing devices
tab_143 <- matrix(table(pathway5_group$q0143),dimnames=list(c('hospital','family doctor office','audiologists office','retail store','none of these'),'Do you use hearing aids or other hearing devices?'))

return(list(tab_137,tab_141,tab_142,tab_151_1,tab_151_2,tab_151_3,tab_151_4,tab_151_5,tab_151_6,tab_151_7,tab_151_8,tab_151_9,tab_143))
#return(list(tab_137,tab_141,tab_142,tab_151_1,tab_151_2,tab_151_3,tab_151_4,tab_151_5,tab_151_6,tab_151_7,tab_151_9))
}

#Plot tables with probabilities for Pathway Questions and hearing loss questions
## Q46 and hcat
grid.table(round(100*prop.table(table(US_data$hcat,US_data$q0046)),digits=1))
grid.table(round(100*prop.table(table(CAN_data$hcat,CAN_data$q0046)),digits=1))
grid.table(round(100*prop.table(table(AUS_data$hcat,AUS_data$q0046)),digits=1))
grid.table(round(100*prop.table(table(UK_data$hcat,UK_data$q0046)),digits=1))
# hcat and q32
grid.table(round(100*prop.table(table(US_data$hcat,US_data$q0032)),digits=1))
grid.table(round(100*prop.table(table(CAN_data$hcat,CAN_data$q0032)),digits=1))
grid.table(round(100*prop.table(table(AUS_data$hcat,AUS_data$q0032)),digits=1))
grid.table(round(100*prop.table(table(UK_data$hcat,UK_data$q0032)),digits=1))

# hcat and q42
grid.table(round(100*prop.table(table(US_data$hcat,US_data$q0042)),digits=1))
grid.table(round(100*prop.table(table(CAN_data$hcat,CAN_data$q0042)),digits=1))
grid.table(round(100*prop.table(table(AUS_data$hcat,AUS_data$q0042)),digits=1))
grid.table(round(100*prop.table(table(UK_data$hcat,UK_data$q0042)),digits=1))



pathway_US <- pathway_response(US_data)
#pathway_CAN <- pathway_response(CAN_data)
#pathway_AUS <- pathway_response(AUS_data)
#pathway_UK <- pathway_response(UK_data)


### MANUAL ASSIGNMENT. Assign each country for table plotting
data <- pathway_US
#data <- pathway_CAN
#data <- pathway_AUS
#data <- pathway_UK


# Plot tables for each country
    table_plot1 <- tableGrob(as.data.frame(data[1]))
    table_plot2 <- tableGrob(as.data.frame(data[2]))
    table_plot3 <- tableGrob(as.data.frame(data[3]))
    table_plot4 <- tableGrob(as.data.frame(data[4]))
    table_plot5 <- tableGrob(as.data.frame(data[5]))
    table_plot6 <- tableGrob(as.data.frame(data[6]))
    table_plot7 <- tableGrob(as.data.frame(data[7]))
    table_plot8 <- tableGrob(as.data.frame(data[8]))
    table_plot9 <- tableGrob(as.data.frame(data[9]))
    table_plot10 <- tableGrob(as.data.frame(data[10]))
    table_plot11 <- tableGrob(as.data.frame(data[11]))
    table_plot12 <- tableGrob(as.data.frame(data[12]))
    table_plot13 <- tableGrob(as.data.frame(data[13]))

## Plots must be manually run in console
grid.arrange(table_plot1,table_plot2,table_plot3,table_plot13)
grid.arrange(table_plot4,table_plot5,table_plot6,table_plot7,table_plot8,table_plot9,table_plot10)
#
```
Explore Hearing loss category distribution from all countries
```{r}



# Run regression model seclection on all US data

AFdata <- US_data
AFdata <- AUS_data
AFdata <- UK_data
AFdata <- CAN_data
boot_ormod_data <- AFdata[,c('hcat','q0002','q0003','q0008','q0012','q0013','q0018_0001','q0032','q0042','q0046')]
boot_ormod_data <-  boot_ormod_data[complete.cases(boot_ormod_data),]
boot_ormod_all <- polr(hcat~factor(q0002)+factor(q0003)+factor(q0008) +factor(q0012)+factor(q0013)+ factor(q0018_0001)+factor(q0032, levels = c(2,1)) + factor(q0042, levels = c(2, 1)) +factor(q0046), data = boot_ormod_data, Hess=TRUE)



dredge_results <- dredge(boot_ormod_all)
subset(dredge_results,delta==0)
ormod_best <- polr(hcat~factor(q0002)+factor(q0003)+factor(q0013)+factor(q0032, levels = c(2,1)) + factor(q0042, levels = c(2, 1)) +factor(q0046), data = boot_ormod_data, Hess=TRUE)
dredge_ortable <- coef(summary(ormod_best))
p <- pnorm(abs(dredge_ortable[,"t value"]),lower.tail=FALSE)*2
dredge_ortable <- cbind(dredge_ortable,'p value'=p)
dredge_ortable




#dredge recommends the following model: Q2+Q3+Q13+Q32,Q42+Q46
dredge_ormod <- polr(hcat~factor(q0002)+factor(q0003)+factor(q0013)+factor(q0032, levels = c(2,1)) + factor(q0042, levels = c(2, 1)) +factor(q0046), data = boot_ormod_data, Hess=TRUE)
summary(dredge_ormod)
dredge_ortable <- coef(summary(dredge_ormod))
p <- pnorm(abs(dredge_ortable[,"t value"]),lower.tail=FALSE)*2
dredge_ortable <- cbind(dredge_ortable,'p value'=p)
dredge_ortable



grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0002))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0003))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0008))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0012))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0013))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0018_0001))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0032))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0042))
grid.table(table(boot_ormod_data$q0046,boot_ormod_data$q0046))

```
