---
title: "AF_RandomSampling_2.5.18"
author: "cmosle1"
date: "2/5/2018"
output: html_document
---

```{r}
#data import. 

AFdata<- read.csv("~/Desktop/Modeling Literature/AF_US_UNI_AllSubsSurvey+Audio_2.20.18.csv", header=T, na.strings="#NULL!")
#head(AFdata)
#View(AFdata)

library("dplyr")
library("tidyr")
library("ggplot2")


```

# Need to: change "90NR" and "9999" to "95"
```{r}

#issue with 90NR --> 95 change: the HHT doesn't measure other thresholds if 90NR at 1000Hz (first threshold tested). Should we set all thresholds to 95 or leave them missing? ---> SOLUTION: SET ALL >90 to 95

#Changing 90NR (aka 9999) and Conventional audio thresholds that are > 90 to 95

#Left Ear
AFdata$L5<-AFdata$L500
AFdata$L5[AFdata$L500 > 90] <- 95
AFdata$L1<-AFdata$L1000
AFdata$L1[AFdata$L1000 > 90] <- 95
AFdata$L2<-AFdata$L2000
AFdata$L2[AFdata$L2000 > 90] <- 95
AFdata$L4<-AFdata$L4000
AFdata$L4[AFdata$L4000 > 90] <- 95


#Right Ear
AFdata$R5<-AFdata$R500
AFdata$R5[AFdata$R500 > 90] <- 95
AFdata$R1<-AFdata$R1000
AFdata$R1[AFdata$R1000 > 90] <- 95
AFdata$R2<-AFdata$R2000
AFdata$R2[AFdata$R2000 > 90] <- 95
AFdata$R4<-AFdata$R4000
AFdata$R4[AFdata$R4000 > 90] <- 95

#At 8000Hz
AFdata$L8<-AFdata$L8000
AFdata$L8[AFdata$L8000 > 90] <- 95
AFdata$R8<-AFdata$R8000
AFdata$R8[AFdata$R8000 > 90] <- 95

#colnames(AFdata)[1000:1020]

#Moving forward, use "L5" --> "R8" instead of "L500"--> "R8000" because the new variables have the 95dB cutoff and 90NR replacements.

```


# Creating PTA Values (L, R, & BE)
```{r}
# Calculating PTA in each ear

#colnames(AFdata[,1000:1021])
AFdata$LPTA <- apply(AFdata[,1011:1014], 1, mean, na.rm=T)
AFdata$RPTA <- apply(AFdata[,1015:1018], 1, mean, na.rm=T)


AFdata$LPTA[is.nan(AFdata$LPTA)]  <- NA
AFdata$RPTA[is.nan(AFdata$RPTA)]  <- NA

#Now can calculate BEPTA (PTA in better ear)
AFdata$BEPTA<- ifelse((!is.na(AFdata$RPTA) & AFdata$RPTA <= AFdata$LPTA) | is.na(AFdata$LPTA),
                      AFdata$RPTA, AFdata$LPTA)
#To Check
#AFdata[c(1,2,257),c("RPTA", "LPTA", "BEPTA")] 
#is.na(AFdata$BEPTA)
#AFdata[which(is.na(AFdata$RPTA)), c("RPTA", "LPTA", "BEPTA")]

```


#Categorizing BEPTA by degree of hearing loss (per ASHA Standards)
```{r}
#ASHA Standards: (0)Normal: -10-25; (1)Mild: 26-40; (2)Moderate: 41-55; (3)Moderately-Severe: 56-70; (4)Severe: 71-90; (5)Profound: >90

AFdata$HLdeg <- cut(AFdata$BEPTA,
                  breaks=c(-Inf, 25, 40, 55, 70, 90, Inf),
                  labels=c("0", "1", "2", "3", "4", "5"))


#just practicing dplyr
AFdata2<-tbl_df(AFdata)
deg2<-AFdata2$HLdeg
lut <- c("0" = "Normal", "1" ="Mild", "2" ="Moderate", "3" = "Moderately-Severe", "4" = "Severe", "5" = "Profound")
AFdata2$HLdegnom <- lut[deg2]
glimpse(AFdata2)

ggplot(data=AFdata, aes(x=HLdeg)) + geom_bar()
ggplot(data=AFdata, aes(x=q0046, y=BEPTA)) + geom_boxplot(aes(group=q0046)) + labs(title="Hearing loss by pathway", x="q0046", y="PTA in Better Hearing Ear")

```



# Relevant Questions
 #q0001- Participant ID
 #q0002- Gender; 1=F
 #q0003- Age: 1= under 60; 2= 60-64; 3=65-69; 4= 70-74; 5= 75-79; 6= 80-84' 70= 85+
 #q0005- marital status: 1=married/committed relationship; 2= single/divorced/widowed/never married
 #q0008- highest grade completed: 1= none; 2=elementary; 3= secondary; 4-undergrad; 5= graduate
 #q0010- household income
 #q0012- do health benefits cover cost of a hearing test
 #q0013- do health benefits cover cost of hearing aids
 #q0014- race: 1= American indian; 2= Asian; 3= White; 4= Native Hawaiian/PI; 5= Black/AA; 6=More than               one race
 #q0030_0015- Have you ever been told by a doctor or HCP that you have hearing loss?
 #q0030_0016- Have you ever been told by a doctor or HCP that you have vision loss? 
 #q0030_0017- Have you ever been told by a doctor or HCP that you have balance problems or dizziness?
 #q0032- Are you deaf or do you have a significant hearing difficulty? 1=Yes; 2=No
 #q0034- Do your ever get noises such as ringing or buzzing in your ears or head (tinnitus) that last         more than 5 minutes? (If yes) Do you get these noises some of the time, most of the time, or         all of the time? 1=No; 2=Yes, some of the time; 3= Yes, most or all of the time
 #q0036- Have you ever worked in a place that was so noisy you had to shout to be heard? 1=No; 2= Yes,         < 1 year; 3=Yes, for 1-5 years; 4= Yes, > 5 years
 #q0042- Do you have a hearing problem now? 1= Yes; 2= No
 #q0046- Pathway question: 1-3= No hearing problem; 4= Hearing loss, no treatment; 5= Hearing loss + treatment
 
 
 
#Creating the random sample of n=250 
```{r}
#Creating first random sample of 250, named "samp1"
set.seed(44)
temp_samp1<- na.omit(sample(1:nrow(AFdata), 250))
samp1<-AFdata[temp_samp1, c("q0002", "q0003", "q0005", "q0008", "q0010", "q0012", "q0013", "q0014", "q0032", "q0034", "q0036", "q0042", "q0046", "BEPTA")]
summary(samp1)
#did not include the q0030_00XX variables because they have no variance (see plot below)
ggplot(AFdata, aes(q0030_0015)) + geom_histogram() 


#Omitting missing PTA and degree of hearing loss variables
usesamp1<- drop_na(samp1, c("BEPTA"))
summary(usesamp1)


ggplot(data=usesamp1, aes(x=BEPTA)) + geom_histogram()
#ggplot(data=temp_samp1, aes(x=HLdeg)) + geom_bar()


#Figure out how to get another sample of 250 that only includes people not in this one to compare
#Find out how to do a dataset split then randomize the split


```


# Relevant Questions
 #q0001- Participant ID
 #q0002- Gender; 1=F
 #q0003- Age: 1= under 60; 2= 60-64; 3=65-69; 4= 70-74; 5= 75-79; 6= 80-84' 70= 85+
 #q0005- marital status: 1=married/committed relationship; 2= single/divorced/widowed/never married
 #q0008- highest grade completed: 1= none; 2=elementary; 3= secondary; 4-undergrad; 5= graduate
 #q0010- household income
 
 #q0012- do health benefits cover cost of a hearing test
 #q0013- do health benefits cover cost of hearing aids
 #q0014- race: 1= American indian; 2= Asian; 3= White; 4= Native Hawaiian/PI; 5= Black/AA; 6=More than               one race
 #q0030_0015- Have you ever been told by a doctor or HCP that you have hearing loss?
 #q0030_0016- Have you ever been told by a doctor or HCP that you have vision loss? 
 #q0030_0015- Have you ever been told by a doctor or HCP that you have balance problems or dizziness?
 #q0032- Are you deaf or do you have a significant hearing difficulty? 1=Yes; 2=No
 #q0034- Do your ever get noises such as ringing or buzzing in your ears or head (tinnitus) that last         more than 5 minutes? (If yes) Do you get these noises some of the time, most of the time, or         all of the time? 1=No; 2=Yes, some of the time; 3= Yes, most or all of the time
 #q0036- Have you ever worked in a place that was so noisy you had to shout to be heard? 1=No; 2= Yes,         < 1 year; 3=Yes, for 1-5 years; 4= Yes, > 5 years
 #q0042- Do you have a hearing problem now? 1= Yes; 2= No
 #q0046- Pathway question: 1-3= No hearing problem; 4= Hearing loss, no treatment; 5= Hearing loss + treatment



#Beginning Amelia
```{r}
#Installing Amelia package for MI. 
#Cite as James Honaker, Gary King, Matthew Blackwell (2011). Amelia II: A Program for Missing Data. Journal of Statistical Software, 45(7), 1-47. URL http://www.jstatsoft.org/v45/i07/.

#install.packages("Amelia")
#update.packages("Amelia")
library('Amelia')
require('Amelia')

summary(lm(BEPTA ~ q0002 + q0003 + q0005 + q0008 + q0010 + q0012 + q0013 + q0014 + q0032 + q0034 + q0036 + q0042 + q0046,
data = usesamp1)) #looking at a comparison between listwise deletion with regression vs. using amelia for imputation


imp1<- amelia(usesamp1, m=5, cs= "q0046", p2s=2)
summary(imp1)

hist(imp1$imputations[[4]]$q0002, col="grey", border="white")
hist(imp1$imputations[[4]]$q0003, col="grey", border="white")
hist(imp1$imputations[[4]]$q0046, col="grey", border="white")



imp2<- amelia(usesamp1, m=5, cs= "q0046", noms = c("q0014"))
              
summary(imp2)
plot(imp2, which.vars= 1:5)
#imputed values are in red, observed in black, non-missing are blue
#q0005 *marital status* is a bad predictor for this model. Also q0010--household income

plot(imp2, which.vars= 6:8)
#take out q0012 & 0013--do health benefits cover cost of hearing test/aids

plot(imp2, which.vars= 10:13)
#variable 9 (q0032) wouldn't run for some reason

usesamp1$q0032
#plot(imp2, 9,col=c("red", "black"), scaled=F, lwd=1)
#Not sure why this won't run... Has only one N/A and the count is the same as q0036... it's binary, but so are some of the other variables

cov(usesamp1)
#assessing covariances to improve model fit 
```

Trying the analysis again, with more imputations and taking out variables mentioned above
```{r}
samp2<-AFdata[temp_samp1, c("q0002", "q0003", "q0008", "q0010", "q0014", "q0034", "q0036", "q0042", "q0046", "BEPTA")]
summary(samp2)

usesamp2<- drop_na(samp2, c("BEPTA"))
summary(usesamp2)


imp3<- amelia(usesamp2, m=8, cs= "q0046", noms = c("q0014"))
summary(imp3)

plot(imp3, which.vars = 1:4) 
plot(imp3, which.vars = 5:9)

overimpute(imp3, var = "q0010")
overimpute(imp3, var = "BEPTA") #Not too bad!
missmap(imp3) #plots missingness by observation

```

#Taking a look at the distributions of my variables

```{r}
ggplot(AFdata, aes(q0002)) + geom_histogram() #dichotomous, so distribution can't be normal
ggplot(AFdata, aes(q0003)) + geom_histogram() #slightly right-skewed
ggplot(AFdata, aes(q0005)) + geom_histogram()
ggplot(AFdata, aes(q0008)) + geom_histogram() #Collapse and dichotomize? Remove completely due to non-representative nature of the in-person sample? Remove this
ggplot(AFdata, aes(q0010)) + geom_histogram() 
ggplot(AFdata, aes(q0012)) + geom_histogram() 
ggplot(AFdata, aes(q0013)) + geom_histogram() #dichotomize? bimodal distribution
ggplot(AFdata, aes(q0014)) + geom_histogram() #race question... very little variance. Dichotomize
table(AFdata$q0014)
ggplot(AFdata, aes(q0032)) + geom_histogram() 
ggplot(AFdata, aes(q0034)) + geom_histogram() 
ggplot(AFdata, aes(q0036)) + geom_histogram()
ggplot(AFdata, aes(q0042)) + geom_histogram()
ggplot(AFdata, aes(q0046)) + geom_histogram()

```

#NEXT STEP: Take an iterative approach by adding one variable at a time to create a more parsimonious model (Forward Selection Model)
